### 2024-04-19 docs/SOSP 2024/intro.tex
Minor edits to intro

Decision forest models are composed of a large collection of decision trees (100-1000), and inference involves 
traversing down each tree in the forest and aggregating the predictions. Inference is typically done in a batched
setting, where multiple inputs are processed simultaneously.
Despite the simplicity of the model and the availability of multiple sources of coarse-grain parallelism (parallelism 
across inputs in a batch and parallelism across trees), existing systems do not consistently scale well across different
models even on the limited set of targets they support. 
%This is because existing systems exploit a limited set of optimizations and often specialize the implementation to a specific hardware platform, and this limits their portability.

@@

%% RG: This may not be needed -- can be removed to save space!
%% \TODO{Oganization}
\begin{itemize}
  \item We identify that there are many different ways to implement  
  decision tree inference and that the best implementation depends both on the model
  and the target. We design a scheduling language that 
  allows us to represent this solution space. 
%   This 
%   scheduling language is expressive enough to represent a wide range of  
%   implementation strategies,  %%.  proposed by prior work.
% %% RG: added CPUs and GPUs. 
%   such as different data layouts, caching strategies, parallel reduction schemes, 
%   that work across CPUs and GPUs. 
  \item We propose a retargetable compiler that can generate code as specified by 
  the schedule. The compiler also includes new abstractions for caching,
  reduction and representing models in memory. These are critical to generate 
  efficient GPU code.
  \item The scheduling language can represent an unbounded number of schedules. 
  We design and implement techniques to search over this space and find high-performance 
  schedules in tens of seconds. 
  \item We exhaustively evaluate \Treebeard{} and report that it achieves 
  portable performance across a range of hardware targets and consistently outperforms
  state-of-the-art decision tree inference frameworks for both CPU and GPU.
\end{itemize}

>>>>

Decision forest models are composed of a large collection of decision trees (typically 100--1000), and inference involves 
traversing down each tree in the forest and aggregating the predictions. Inference is typically done in a batched
setting, where multiple inputs are processed simultaneously.
Despite the simplicity of the model and the availability of multiple sources of coarse-grain parallelism (parallelism 
across inputs in a batch and parallelism across trees), existing systems do not consistently scale well across different
models even on the limited set of targets they support. 
%This is because existing systems exploit a limited set of optimizations and often specialize the implementation to a specific hardware platform, and this limits their portability.

@@

%% RG: This may not be needed -- can be removed to save space!
%% \TODO{Oganization}
In summary, this paper makes the following contributions.
\begin{itemize}
  \item We identify that there are many different ways to implement  
  decision tree inference and that the best implementation depends both on the model
  and the target. We design a scheduling language that 
  allows us to represent this solution space. 
%   This 
%   scheduling language is expressive enough to represent a wide range of  
%   implementation strategies,  %%.  proposed by prior work.
% %% RG: added CPUs and GPUs. 
%   such as different data layouts, caching strategies, parallel reduction schemes, 
%   that work across CPUs and GPUs. 
  \item We propose a retargetable compiler that can generate code as specified by 
  the schedule. The compiler also includes new abstractions for caching,
  reduction and representing models in memory. These are critical to generate 
  efficient GPU code.
  \item The scheduling language can represent an unbounded number of schedules. 
  We design and implement techniques to search over this space and find high-performance 
  schedules in tens of seconds. 
  \item We exhaustively evaluate \Treebeard{} and report that it achieves 
  portable performance across a range of hardware targets and consistently outperforms
  state-of-the-art decision tree inference frameworks for both CPU and GPU.
\end{itemize}
